Supplementary Information

### 2020-08-04 doc/manuscript/MEE_manuscript.Rmd
add sites

Kristina J. Anderson-Teixeira^1,2^*,
Valentine Herrmann^1^,
Christy Rollinson^#^,
Erika B. Gonzalez-Akre^1^,
Bianca Gonzalez^1^,
Neil Pederson^#^,
Camille Piponiot^1,2^,
Ross Alexander^#^,
Craig D. Allen,
Raquel Alfaro-Sánchez,
Jennifer Baltzar,
Patrick Baker,
Justin Cooper,
Ryan Helcoski^1^,
Vasickova Ivana,
Kaspar Jakub,
Kamil Kral,
James Lutz,
Ellis Q. Margolis,
Justin Maxwell,
Sean McMahon,
Helene Muller-Landau,
Samonil Pavil,
Anastasia Sniderhan,
Alan J. Tepley^1,#^,
Mart Vlam,
Peter Zuidema

>>>>

Kristina J. Anderson-Teixeira^1,2^*,
Valentine Herrmann^1^,
Christy Rollinson^#^,
Erika B. Gonzalez-Akre^1^,
Bianca Gonzalez^1^,
Neil Pederson^#^,
Camille Piponiot^1,2^,
Ross Alexander^#^,
Craig D. Allen,
Raquel Alfaro-Sánchez,
Taia Awada,
Jennifer Baltzar,
Patrick Baker,
Paulo Cherubini,
Justin Cooper,
Ryan Helcoski^1^,
Vasickova Ivana,
Kaspar Jakub,
Kamil Kral,
James Lutz,
Ellis Q. Margolis,
Justin Maxwell,
Sean McMahon,
Helene Muller-Landau,
Samonil Pavil,
Sabrina Russo,
Anastasia Sniderhan,
Alan J. Tepley^1,#^,
Mart Vlam,
Peter Zuidema
